### 2018-06-28 paper/2-background.tex
Restarting schedulers are not minimal

\Bazel is one of the first examples of openly available cloud build systems.
As of writing, it is not possible to express dynamic dependencies in
user-defined build rules, however some of the predefined build rules require
dynamic dependencies and the internal build engine can cope with them by using
a \emph{restarting} task scheduler, which is similar to that of \Excel but does
not use the calc chain. \Bazel is minimal and supports the early cutoff
optimisation.

@@

\begin{table}[h]
\smaller
\centering
\begin{tabular}{l||l|l||l|c|c|c}
\hline
$\!$Build system$\!$& Persistent build information & Algorithm   & Dependencies   & Minimal & Cutoff & Cloud$\!$\\\hline
$\!$\Make       $\!$& File modification times      & Topological & Static         & Yes     & No     & No   $\!$\\
$\!$\Excel      $\!$& Dirty cells, calc chain      & Restarting  & Dynamic        & No      & No     & No   $\!$\\
$\!$\Shake      $\!$& Previous dependency graph    & Suspending  & Dynamic        & Yes     & Yes    & No   $\!$\\
$\!$\Bazel      $\!$& Cloud cache, command history & Restarting  & Static$^{(*)}$ & Yes     & Yes    & Yes  $\!$\\\hline
\hline
\end{tabular}
\vspace{0.5mm}
\caption{Summary of build system differences; $^{(*)}$predefined build rules can
have dynamic dependencies.\label{tab-summary}}
\vspace{-6mm}
\end{table}

>>>>

\Bazel is one of the first examples of openly available cloud build systems.
As of writing, it is not possible to express dynamic dependencies in
user-defined build rules, however some of the predefined build rules require
dynamic dependencies and the internal build engine can cope with them by using
a \emph{restarting} task scheduler, which is similar to that of \Excel but does
not use the calc chain. \Bazel is not minimal in the sense that it may restart a
task multiple times as new dependencies are discovered and rebuilt, but it
supports the early cutoff optimisation.

@@

\begin{table}[h]
\smaller
\centering
\begin{tabular}{l||l|l||l|c|c|c}
\hline
$\!$Build system$\!$& Persistent build information & Algorithm   & Dependencies   & Minimal & Cutoff & Cloud$\!$\\\hline
$\!$\Make       $\!$& File modification times      & Topological & Static         & Yes     & No     & No   $\!$\\
$\!$\Excel      $\!$& Dirty cells, calc chain      & Restarting  & Dynamic        & No      & No     & No   $\!$\\
$\!$\Shake      $\!$& Previous dependency graph    & Suspending  & Dynamic        & Yes     & Yes    & No   $\!$\\
$\!$\Bazel      $\!$& Cloud cache, command history & Restarting  & Static$^{(*)}$ & No      & Yes    & Yes  $\!$\\\hline
\hline
\end{tabular}
\vspace{0.5mm}
\caption{Summary of build system differences; $^{(*)}$predefined build rules can
have dynamic dependencies.\label{tab-summary}}
\vspace{-6mm}
\end{table}
